
\documentclass{resume} % Use the custom resume.cls style
\usepackage[left=0.4 in,top=0.4in,right=0.4 in,bottom=0.4in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}} 
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{PRATIK MISHRA} % Your name
\address{+1 (678) 436-1989 \\ pmishr14@asu.edu \\ linkedin.com/in/ipratikmishra \\ github.com/ipratikmishra \\ www.pratikm.com}  % Your phone number and email

\begin{document}

\begin{rSection}{Education}

{\bf Master’s, Computer Science} \hfill {May 2019}
\\ 
Arizona State University, Tempe, Arizona  \hfill{GPA:3.56/4.0}
\\\textit{Relevant Coursework: Distributed Database Systems, Statistical Machine Learning, Data Mining\\
Mobile Computing, Foundation of Algorithms, Software Security, Software Verif/Validation/Test.}

{\bf Bachelor of Engineering, Information Technology} \hfill {June 2017}
\\ 
International Institute of Information Technology, India \hfill {GPA:7.83/10.0}

\end{rSection}


\begin{rSection}{TECHNICAL SKILLS}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Programming & Java, Python, C++\\ 
Big Data & Hadoop, Map Reduce, Spark, Kafka\\
Web Technologies & JavaScript, HTML5, CSS3, PHP, AJAX, REST Services\\
Frameworks & React, Redux, Angular, Node.js (Express), ASP.NET MVC, Android\\
Database & MySQL, Oracle 11g, MongoDB, PostgreSQL\\
Tools & Git, Bash, Gulp, VS Code, Maven, JUnit, Eclipse, Talend\\

\end{tabular}

\end{rSection}

\begin{rSection}{WORK EXPERIENCE}

\begin{rSubsection}{Walgreens Boots Alliance}{June 2018 - August 2018}{Software Engineering Intern}{Chicago, IL} 

\item Backend development for the Rx Renewal team undertaking world's largest pharmacy renewal program (150 million patients and 12 million prescribers).
\item Built a Spring Boot RESTful micro service that invokes a SOAP-based service-broker to search prescriptions from IC+ DB.
\item Devised a client application with Angular 5 that uses REST API to search and display the Rx records in the dashboard.
\item Developed Talend ETL jobs to extract and transform GBs of data and upload to Kafka topics on the cluster.
\\\textit{Environment: Java, Angular, Spring Boot, Kafka, REST, SOAP, Talend.}

\end{rSubsection} 

\begin{rSubsection}{Arizona State University - Herberger Institute}{October 2017 – Present}{Full Stack Web Developer}{Tempe, AZ}
\item Responsible for developing and refactoring a multitude of web applications for ASU’s design school.
\item Working in a fast-paced Agile Scrum environment with daily stand-up meetings. 
\item Documenting failures of custom developed solutions and implementing corrective solutions. 
\\\textit{Environment: ASP.NET MVC, Angular, HTML5, CSS3, Bootstrap, JavaScript, MySQL, JIRA.}
\end{rSubsection} 

\begin{rSubsection}{Shamuka Software Inc.}{May 2016 – July 2016}{Software Engineering Intern}{Palo Alto, CA} 

\item Developed a React SPA for scheduling, forum, and pricing for fitness studios based in San Francisco.
\item Implemented front-end components using React JavaScript and used Redux to maintain application state.
\item Used REST API to parse objects from JSON hosted in an AWS environment.
\item  Added authentication components using OAuth from social login APIs.
\\\textit{Environment: React, Redux, ES6, Bootstrap, Babel, Webpack.}
\end{rSubsection} 

\end{rSection}
\begin{rSection}{TECHNICAL PROJECTS} 

\begin{rSubsection}{Gesture Recognition System for American Sign Language}{Spring 2018}{}

\item Implemented feature extraction and feature deduction from the gesture dataset obtained from various sensors of a MYO wristband. A model was created, trained and tested with the data to recognize over 20 ASL symbols.
\end{rSubsection}

\begin{rSubsection}{Identifying Hotspots in New York using Distributed Database}{Fall 2017}{}

\item Implemented an algorithm to identify a list of the fifty most statistically significant spatial hot spots from the collection of New York City yellow cab taxi trip data-set. The data was collected and pushed into the Hadoop File System and Spark functions were designed and developed to calculate the hotspots.
\end{rSubsection}

\begin{rSubsection}{BraiNet – Privacy management Android App}{Fall 2017}{}

\item Android application that uses brain signals through a brain sensor for authentication in smartphones. Similar to Face ID in iPhone X, but uses brain signals to authenticate.
\end{rSubsection}

\begin{rSubsection}{PatientTracker Android App}{Spring 2017}{}

\item Developed a health management android application to track patient health records like various illnesses, medicines prescribed and other vital records that can be used by a doctor to perform diagnosis.
\end{rSubsection}

\end{rSection} 
\end{document}
